Lesson 3
========================================================

***

### What to Do First?
Notes:

Nothing to note

***

### Pseudo-Facebook User Data

Notes:


```{r Pseudo-Facebook User Data}
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
#library(ggplot2)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)
names(pf)
qplot(x = dob_day, data = pf) + 
  scale_x_continuous(breaks = 1:31)

```

***

#### What are some things that you notice about this histogram?
Response:

1st day of month has more dob than usual and opposite with 31st.

***

### Moira's Investigation
Notes:

Calculate Percentage and Number of responses of friend to a post  

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:  
My codechef global rank   
my checkin   

#### How many of your friends do you think saw that post?
Response:   
number :- 80   

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?  
Response:   
percentage :- 35   

***

### Perceived Audience Size
Notes:    
People guesses are quater of actual size
  
***

### Faceting
Notes:
   
```{r Faceting}
ggplot(data = pf, aes(x = dob_day)) + 
  geom_histogram(binwidth = 1) + 
   scale_x_continuous(breaks = 1:31) + 
   facet_wrap(~dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:    
1st day of jan month have more date of birth than other days of year.

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:

#### Which case do you think applies to Moira’s outlier?    
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
names(pf)
qplot(data = pf, x = friend_count)
```

#### How is this plot similar to Moira's first plot?
Response:    
As like as Moira's first plot this plot has the peaks at lower number of friends.

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
#qplot(data = pf, x = friend_count, xlim = c(0,1000))
qplot(data = pf, x = friend_count) +
    geom_histogram() +
    scale_x_continuous(limits = c(0,1000))
```

### Exploring with Bin Width
Notes:

Most of the guesses are 10,20,50 and other regular numbers.

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
qplot(data = pf, x = dob_year) +
  geom_histogram(binwidth = 1, color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(1980,2000,1), limits = c(1980,2000))
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:   
women

#### What's the difference between the median friend count for women and men?
Response:    
22

#### Why would the median be a better measure than the mean?
Response:    
Outlier   

***

### Tenure
Notes:

```{r Tenure}
qplot(x = tenure, data = pf) +
  geom_histogram(binwidth = 30, color = I('black'), fill = I('#099DD9'))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf) +
  geom_histogram(binwidth = 0.25, color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(1,7,1), limits = c(1,7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x = tenure/365, data = pf, xlab = "Number of Years using Facebook" ,ylab = "Number of User in sample") +
  geom_histogram(binwidth = 0.25, color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(breaks = seq(1,7,1), limits = c(1,7))

```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age, data = pf, xlab =" Ages " ,ylab = "Number of User in sample") +
  geom_histogram(binwidth = 2, color = I('black'), fill = I('#099DD9')) +
 scale_x_continuous(breaks = seq(1,80,2), limits = c(1,80))

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

```{r Transforming Data}
p1 <- qplot(data = pf, x = friend_count )
summary(log10(pf$friend_count))
summary(log10(pf$friend_count+1))

summary(sqrt(pf$friend_count))

p2 <- qplot(data = pf, x = friend_count+1 ) +
  scale_x_log10()
p3 <- qplot(data = pf, x = friend_count) +
  scale_x_sqrt()
library(gridExtra)
grid.arrange(p1,p2,p3)
#Or we can use this method
#q1 <- ggplot(data = pf, aes( x = friend_count)) + geom_histogram()
#q2 <- q1 + scale_x_log10()
#q3 <- q1 + scale_x_sqrt()
#grid.arrange(q1,q2,q3)
```

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons} 
library(ggplot2)
qplot(data = subset(pf,!is.na(gender)), x = friend_count,
      y = ..count../sum(..count..),
      xlab = "Friend Count",
      ylab = "Proportion of Users with that friend count",
      binwidth = 10, geom = "freqpoly", color = gender) + 
  scale_x_continuous(breaks = seq(0,1000,50), limits = c(0,1000)) +
  scale_x_log10()
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
qplot(data = subset(pf, !is.na(gender)),
       x = www_likes,
      geom = "freqpoly", color = gender) +
  scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,100)) +
  scale_x_log10()
by( pf$www_likes, pf$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)),
      geom = "boxplot")
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)),
      geom = "boxplot") + 
  coord_cartesian(ylim = c(0,1000))

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friendships_initiated, data = subset(pf, !is.na(gender)),
      geom = "boxplot") +
  coord_cartesian(ylim = c(0,150))
by(pf$friendships_initiated, pf$gender, summary)

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(pf$mobile_likes)
summary(pf$mobile_likes > 0)

mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0,1,0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)
sum(pf$mobile_check_in == 1)/length(pf$mobile_check_in)
```

Response:

***

### Analyzing One Variable
Reflection:

1. Learn to create histogram using qplot.
2. facet_wrap function.
3. Coloring the histograms.
4. Making frequency Polygons.
5. Make boxplot and analyse the data using it.
6. table(),by() and summary() functions.
7. and many other things.

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!